Pretty darn good control: when are approximate solutions better than approximate models

### 2023-01-09 manuscript/manuscript.Rmd
TAC, variable prefactor, etc

*Total allowable catch (TAC)* is one such policy.
It consists on reducing the inclination of the line defined by $h(F)$, for example using $h(F) = 0.8\times r/2$.

>>>>

*Total allowable catch (TAC)* is one such policy.
It consists on reducing the inclination of the line defined by $h(F)$ using a prefactor $\alpha$ in $h(F) = \alpha\times rF/2$. 
Plausible examples are $\alpha = 0.8$ or $0.9$.
Another common alternative is to have a prefactor $\alpha = \alpha(F)$ which decreases from one to zero as $F$ decreases below a threshold:
$$
  h(F) = \alpha(F)\times rF/2,
$$
where,
$$
  \alpha(F) = \begin{cases}
  1, \qquad &\text{if } F > F_{\text{thresh.}},\\
  F / F_{\text{thresh.}}, \qquad & \text{else}.
  \end{cases}
$$
